

```{r, include=FALSE}
setwd("C:/Users/mcolvin/Documents/projects/Age and Growth/Analysis/Sample Type Bias")
  source("./src/1_global.R")  	
	source("./src/2_functions.R")         
	source("./src/3_load.R")     
  source("./src/4_clean.R")
 	source("./src/5_tables.R")
	source("./src/6_figures.R") 
```


# How does sampling type effect parameter estimate bias and precision?

## Introduction

The parameters of a von Bertalanffy growth function are commonly estimated given 
age-length data for individual fish.  These parameters are used to assess growth, 
mortality, and production of a fish population.  These parameters are also used 
to estimate mortality and production.  
* uncertainty (i.e., se is not of concern)


## Objectives

The objectives of this analysis were to compare the effect of simple random  
sampling (srs), binning, age length key expansion, and reweighting on 
parameter estimates and uncertainty.  

The expectation was that parameter estimate bias should not be 
terrible but the uncertainty around the estimates may be overly 
precise.  In other words, non-random sampling will likely result 
in over estimation of precision.   

## Methods

Overview.&mdash;A simulation was used to compare parameter estimates of a 
VBGF among the 4 sampling strategies.  The simple random sample is unbiased 
and was used as the baseline to evaluate bias in parameter estimates and uncertainty.  

True population.&mdash;A reference true population was generated and simple 
random sample. We used the same population parameters used by C  for two life-history types: 
short-lived high-productivity (SLHP) and long-lived low-productivity (LLLP) species

$L_{\infty}$ was ....  
$K$ was 
$t_0$ was 0 

$L_{age}=L_{\infty}\cdot e^{-k\cdot(age-t_0)}$  

error:  
$e_i \sim N(0,\sigma)$ or  
$e_i \sim e^{N(0,\sigma)}$  

Sample size was same as Coogins


Sampling strategies.&mdash;    
1. Binning
2. Age length key expansion
3. Rewighting

#### Analysis

## Results

* binning: as the number of indviduals per bin is small the sample converges to a random sample.  
In other words the effect of 'binning', if there are only a couple of full bins 

### Reference dataset

### Bias and precision

## Figures

```{r,echo=FALSE}
figures(1)
```

Figure 1.  Effect of sampling type and estimation on the distribution of point estimates of Linf, k, and t0 for a short lived, small bodied, fast growing fish.  The dotted line denotes the true value.  


```{r,echo=FALSE}
figures(2)
```

Figure 2.  Effect of sampling type and estimation on the distribution of standard error estimates for Linf, k, and t0 for a short lived, small bodied, fast growing fish.  The dotted line denotes the true value.  


```{r,echo=FALSE}
figures(3)
```

Figure 3.  Effect of sampling type and estimation on the distribution of point estimates of Linf, k, and t0 for a long lived, large bodied, slow growing fish.  The dotted line denotes the true value.  


```{r,echo=FALSE}
figures(4)
```

Figure 4.  Effect of sampling type and estimation on the distribution of standard error estimates for Linf, k, and t0 for a long lived, large bodied, slow growing fish.  The dotted line denotes the true value.  

## Tables  

```{r, echo=FALSE}
kable(vbgf_parms)
```
